% Please compile the tex file by pdfLaTeX, 
% it would handle the landscape pages correctly.
\documentclass[12pt]{mines-thesis}
% Font Size: 10-12 point type, change the value above

%========================================
%                              Set-up                              
%========================================
% Text will be double spaced or 1.5 spaced. 
%\OnehalfSpacing 
\DoubleSpacing
% Set the indentation of each paragraph.
\setlength{\parindent}{2em}
% Set the lowest level to show in the table of contents
\maxtocdepth{subsubsection}
% Set the fully-justified or left-justified text
%\textalignment{fully-justified}
%\textalignment{left-justified}
% Arial font
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}
% Arial font MUST COMPILE WITH xelatex
%\usepackage{fontspec}
%\setmainfont{Arial}

\include{Chapters/settings}

\begin{document}
%========================================
%                            Front Matter                              
%========================================
\autotitle %automatically change the title into upper cases and reshape it to an inverted pyramid
%\title{Thesis title centered on the page vertically and horizontally, in all upper case letters and in an inverted pyramid shape. Math mode: $\frac{2^{15}}{\pi}$}
% If you want to break the title by yourself, you must use ``\protect\\ ''.
% For example,
\title{
	Security and Privacy on Smartphones:\protect\\  A Sensing Approach
}
	
\author{Ming Li}  % this is your name exactly as you want it
\year{2020}     % this is the year of defence
\degree{Doctor of Philosophy}{Computer Science} %
\advisor{Dr. Dejun Yang}
%\coadvisor{Dr. Co-Advisor}  % comment out this line  if no co-advisor
\department{Department of Computer Science}
\departmenthead{Dr. Tracy Camp}
	
	
%==================Abstracts===============
% 1. Are generally 200-300 words in length, 
% 2. Consist of one to two paragraphs of information,
% 3. Does not usually contain citations, 
% 4. Do not repeat the thesis title, and
% 5. Each paragraph should be indented.	
\begin{abstract}
The technological advancements have made smartphones an indispensable component of our daily lives. Security and privacy (S\&P) on smartphones has thus become an important research topic. 
Since there are no universally applicable solutions to solve S\&P issues on smartphones, we conduct our research in a case study manner, with a focus on smartphone sensors. 
%
We propose {\spp} to show how smartphones get eavesdropped  by motion sensors, {\uu} to authenticate users with gestures in the air, and {\mv} to protect  voice authentication systems against spoofing attacks.

%
In detail, the {\systemName} system turns smartphones into spy bugs by performing {\attackName} attack.  Such an attack is  based on the fact that motion sensors (accelerometers and gyroscopes) can measure audio signals, though at a much lower sampling rate. It is a big threat to smartphone users since the phone's operating system grants applications permissions to motion sensors automatically.
 %
 
{\uu} uses the microphones and speakers in smartphones to send ultrasound signals and catch users' finger movements, then utilizes these user-specific movements to unlock the phone. It is a great alternative to the password/fingerprint authentication when users' fingers are dirty or wet and to the face authentication when users wear masks or goggles.
%


 {\shortname} is a spoof-proof voice authentication system that not only authenticates users by their voices but also differentiates live people and electronic devices. In other words, attackers are unable to unlock the phone by replay attack (attackers record the victim's voice in person or online, then replay the recording and access the victim's devices illegally). The idea is to utilize the self demodulation effect and acoustic attenuation effect that occurred when sound signals transmit through human bodies. Motion sensors are used to catch such signals.
 
\end{abstract}

%%============Acknowledgements==============
% Comment the section out if you don't need it 
\begin{acknowledgment}
	First and foremost, I would like to express my deepest appreciation to Dr.~Dejun Yang, without whom this thesis would not have been possible. Dr.~Yang is not only my advisor, but he is also my mentor who gave his endless support and encouraged me to go through all the difficulties throughout my masters and doctoral programs.
	%
	I would also like to thank my committee members, Dr.~Tracy Camp, Dr.~Michael Wakin, and Dr.~Hao Zhang,  not only for their time and support, but also for their valuable comments and insightful questions. 
	%
	Thanks should also go to all my friends at Mines. Special thanks to my research group members, Dr.~Jian Lin, Yuhui Zhang, and Nan Jiang.  It is a great pleasure of studying and working with them. Pursuing a Ph.D. is difficult, but they make the journey no longer lonely. 
	%
	Lastly, I would like to thank my family and extended family. Near or far, they have always being there for me. Words are powerless to express my gratitude.
	
	
%	 I am grateful for all the memories I carry with me, for the wonderful moments that had such an impact in my life 'till this day.
	
%	
%	Thank you, advisor, committee members,friends, family members etc.
%	
%	 Thanks to my advisor: Dejun Yang
%	 Committee members: Tracy Camp, Michael Wakin, and Hao Zhang
%	 Research group members: Nan Jiang, Jian Lin, and Yuhui Zhang
%	 Family and friends
%	 Thanks to everyone in the computer science department and everyone else for attending
	 
	 
\end{acknowledgment}

%%==================Dedication===============
% Comment the section out if you don't need it 
\begin{dedication}
	\begin{vplace}
	\centering
	\vspace{-1in}
	For my love, X.
	\end{vplace}
\end{dedication}	


\makefrontmatter


%========================================
%                              Main Body                              
%========================================
%TODO Main Body
	
% You can separate the chapters to different files

\include{Chapters/chapterIntro}
\include{Chapters/chapterSpyPhone}
\include{Chapters/chapterUltraUnlock}
\include{Chapters/chapterMoVo}
\include{Chapters/chapterConcl}


	
%========================================
%                             Back Matter                               
%========================================
%%================Reference===============
% You may:
% 1. Add one reference section at the end of the thesis/dissertation, 
% or 
% 2. Add a reference section at the end of each chapter
% Set the NAME of your bibliography file
\bibliography{References/referenceAll.bib} 
% Set the STYLE of your reference, you need to compile TWICE
% entries are sorted alphabetically and labelled with numbers.
\bibliographystyle{plain}
% Chicago style is an "author-date" style, so the citation in the text consists of the author(s) name and year of publication given wholly or partly in round brackets.
%\bibliographystyle{chicago}	 % Require natbib package

%%=================Appendix===============
% The \appendix declaration changes the numbering of chapters 
% to an alphabetic form and also changes the names of chapters 
% from \chaptername (default  CHAPTER) to the value 
% of \appendixname (default APPENDIX). 
%\appendix 
%\include{Chapters/appendixA}
%\include{Chapters/appendixB}

\end{document}